

---
title: "Getting started with textSpan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with textSpan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
library(httr)
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

# textSpan quickstart guide
R package to measure  textual spanning on a document by document similarity matrix .

Load the textSpan package and additional packages needed for visualizations.
```{r}
install_github("dustin-stoltz/textSpan")

library(pacman)
pacman::p_load(pluralize, ggplot2, ggrepel, ggExtra, Hmisc, plyr, RColorBrewer, 
               colorRamps, tidyverse, grid, ggridges)
```

The `textSpan` function is a measure which increases when a document is similar to documents which are not also similar to each other. This is defined by the following equations:

(\$$S(i) = \sum_j (p_{ij} + \sum_q p_{iq} p_{qj})^2$$\)

# Simulated Examples

Using 

# Empirical Examples

## Using document by term frequency matrix

## Using document by topic probability matrix

